Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-02 paper.tex
Comments on basic results

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performs regarding each class. Therefore, precision and recall rates are examined for each class. \\

>>>>

The developed classifiers are assessed by measuring their accuracy and the precision and recall of each class label. Evaluation measures for all classifiers are shown in Table \ref{table:basic_classifiers}. It can be noticed that all classifiers have obtained very close accuracy ratios with a slight advantage for the MLP network with 71\% accuracy. In general, accuracy rates don't give an insight on how the classifier performs regarding each class. Therefore, precision and recall rates are examined for each class. Precision and recall values in Table \ref{table:basic_classifiers} show that J48 classifier achieved the highest recall value of 72\% for (VH) class with 74\% precision. The second best classifier for this important class is MLP with 68\% recall and 77\% precision. Having a look at the second important class which is (H), we can see that MLP has the highest recall with 65\% and a precision of 62\%. J48 comes second for the (H) class with a slight decrease in the recall value.
